Rank Product Tests

### 2021-07-17 R/rank_product_md.Rmd
RP test for youth qualifiers

# Computing the Rank-Product For Qualifiers

>>>>

# Computing the Rank-Product For Qualifiers
```{r}
n_perm <- 1000
# Rank Product for Finals (n = 6, k = 3)
fin_perms <- lapply(1:n_perm, function(x) assign_ranks(21) %>% mutate(rp = total^(1/3))
                    )

# list of rank-products for each total rank
rp_sets <- lapply(1:21, function(r) sapply(fin_perms, function(x) x$rp[r])
                  )
```

## Men's Qualifiers
```{r}
E_m <- sapply(1:21, function(x) mean(m_qual_rp$rp[x] >= rp_sets[[x]]) # false discovery rate: /x
              )
```

```{r, echo = FALSE}
data.frame(last = m_qual_rp$last
           , first = m_qual_rp$first
           , rank = m_qual_rp$rank
           , rp = m_qual_rp$rp
           , pval = E_m
           ) %>% 
  knitr::kable()
```

## Women's Qualifiers
```{r}
E_f <- sapply(1:21, function(x) mean(f_qual_rp$rp[x] >= rp_sets[[x]]) # false discovery rate: /x
              )
```

```{r, echo = FALSE}
data.frame(last = f_qual_rp$last
           , first = f_qual_rp$first
           , rank = f_qual_rp$rank
           , rp = f_qual_rp$rp
           , pval = E_f
           ) %>% 
  knitr::kable()
```
